Future Cosmic Microwave Background delensing with galaxies surveys

### 2017-07-25 Notes/galaxies_delensing_uchicago_thesis.tex
keep it up to data
text: conclusions

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/BB_res_ell2.pdf}
\caption{Here we illustrate the effect of delensing on the B-mode power spectrum. The red solid line corresponds to the fiducial lensing B-mode component of the signal while the dashed green line corresponds to the inflationary one for the higher amplitude allowed by current experiments.
The residual power left after delensing for some of the LSS tracers described in \refsec{model}. 
The rapid improvement in the level of instrumental noise (dashed curves for SPTPol and CMB S4) will require a high level of delensing to exploit these experiments fully.}
\label{fig:bbplot}
\end{center}
\end{figure}

@@

% ===================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/compare_kernel.pdf}
\caption{\textbf{Kernels Comparison}: Comparison of the different kernels as a function of redshift for some of the tracers used in this analysis. The bigger the overlap with the CMB lensing kernel the better the reconstruction of the lensing potential will be leading to a higher delensing efficiency. }
\label{fig:kernel}
\end{center}
\end{figure}
% ===================

@@

% ===================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/compare_kernel_tomo.pdf}
\caption{\textbf{Kernels Comparison with tomographic bins}: Comparison of the 10 LSST  tomographic bins together with the full LSST survey and the CMB lensing kernel. 
Compared to a full survey approach, tomographic binning allows to optimally weight different bins according to their cross correlation with the CMB lensing. This leads to a better delensing efficiency. }
\label{fig:kerneltomo}
\end{center}
\end{figure}
% ===================

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/B_res_bin.pdf}
\caption{Tomographic bins improve the cross-correlation of galaxy surveys with CMB lensing. Here we show the cross-correlation coefficient (\refeq{rho1}) as a function of angular scale for full surveys (solid lines) and tomographically binned surveys (dot-dashed line).}
\label{fig:rho-tomo}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/actual_scenario_planck.pdf}
\caption{Correlation factor between current galaxy survey and internally reconstructed $\phi$ CMB lensing potential as a function of the angular scale $\ell$. 
The dashed curve corresponds to (with arbitrary scale) $C^{\kappa \kappa} \times \frac{\partial C^{BB}}{\partial{C^{\kappa \kappa}}}$, showing which scales contribute to the $\ell<100$ B-mode power.}
\label{fig:corrnow-planck}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/actual_scenario.pdf}
\caption{Correlation factor between current galaxy survey and internally reconstructed $\phi$ CMB lensing potential as a function of the multipole $\ell$. }
\label{fig:corrnow}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/S3_scenario.pdf}
\caption{Correlation factor. Same as \reffig{corrnow} but for stage 3 experiments. }
\label{fig:corrS3}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/S4_scenario.pdf}
\caption{Correlation factor. Same as \reffig{corrnow} but for stage 4 experiments. }
\label{fig:corrs4}
\end{center}
\end{figure}

@@

% ===================
%\onecolumngrid
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/errors_summary.pdf}
\caption{\relook{to be filled with final results}}
\label{fig}
\end{center}
\end{figure}
\twocolumngrid

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/BB_res_ell2_thesis.pdf}
\caption{Here we illustrate the effect of delensing on the B-mode power spectrum. The red solid line corresponds to the fiducial lensing B-mode component of the signal while the dashed green line corresponds to the inflationary one for the higher amplitude allowed by current experiments.
The residual power left after delensing for some of the LSS tracers described in \refsec{model}. 
The rapid improvement in the level of instrumental noise (dashed curves for SPTPol and CMB S4) will require a high level of delensing to exploit these experiments fully.}
\label{fig:bbplot}
\end{center}
\end{figure}

@@

% ===================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/compare_kernel_thesis.pdf}
\caption{\textbf{Kernels Comparison}: Comparison of the different kernels as a function of redshift for some of the tracers used in this analysis. The bigger the overlap with the CMB lensing kernel the better the reconstruction of the lensing potential will be leading to a higher delensing efficiency. }
\label{fig:kernel}
\end{center}
\end{figure}
% ===================

@@

% ===================
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/compare_kernel_tomo_thesis.pdf}
\caption{\textbf{Kernels Comparison with tomographic bins}: Comparison of the 10 LSST  tomographic bins together with the full LSST survey and the CMB lensing kernel. 
Compared to a full survey approach, tomographic binning allows to optimally weight different bins according to their cross correlation with the CMB lensing. This leads to a better delensing efficiency. }
\label{fig:kerneltomo}
\end{center}
\end{figure}
% ===================

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/B_res_bin_thesis.pdf}
\caption{Tomographic bins improve the cross-correlation of galaxy surveys with CMB lensing. Here we show the cross-correlation coefficient (\refeq{rho1}) as a function of angular scale for full surveys (solid lines) and tomographically binned surveys (dot-dashed line).}
\label{fig:rho-tomo}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/actual_scenario_planck_thesis.pdf}
\caption{Correlation factor between current galaxy survey and internally reconstructed $\phi$ CMB lensing potential as a function of the angular scale $\ell$. 
The dashed curve corresponds to (with arbitrary scale) $C^{\kappa \kappa} \times \frac{\partial C^{BB}}{\partial{C^{\kappa \kappa}}}$, showing which scales contribute to the $\ell<100$ B-mode power.}
\label{fig:corrnow-planck}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/actual_scenario_thesis.pdf}
\caption{Correlation factor between current galaxy survey and internally reconstructed $\phi$ CMB lensing potential as a function of the multipole $\ell$. }
\label{fig:corrnow}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/S3_scenario_thesis.pdf}
\caption{Correlation factor. Same as \reffig{corrnow} but for stage 3 experiments. }
\label{fig:corrS3}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/S4_scenario_thesis.pdf}
\caption{Correlation factor. Same as \reffig{corrnow} but for stage 4 experiments. }
\label{fig:corrs4}
\end{center}
\end{figure}

@@

% ===================
%\onecolumngrid
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2,clip]{../images/errors_summary_thesis.pdf}
\caption{\relook{to be filled with final results}}
\label{fig}
\end{center}
\end{figure}
